Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-11-11 xrb2/paper.tex
Updates to XRB2 flame speed plots

\begin{figure}[t]
	\centering
	\plotone{flame_speeds_rotation.pdf} % Not certain what style we want for the plot here
	\caption{\label{fig:flame_speeds_1} Plots of flame front position vs.\ time for the 500 Hz and 1000 Hz runs. The dashed lines
		show quadratic least-squares fits to the data for $t \gtrsim 20~\mathrm{ms}$.}
\end{figure}

\begin{figure}[t]
	\centering
	{\color{red} Placeholder for the flame speed plot that shows temperature dependence}
	\caption{\label{fig:flame_speeds_2} Plots of flame front position vs.\ time for the three 500 Hz runs with
		$T_{star} \leq 3 \times 10^8~\mathrm{K}$. The dashed lines show quadratic least-squares fits to the data
		for $t \gtrsim 20~\mathrm{ms}$.}
\end{figure}

>>>>

\begin{figure}[t]
	\centering
	\plotone{flame_speeds_rotation.pdf} % Not certain what style we want for the plot here
	\caption{\label{fig:flame_speeds_1} Flame front position vs.\ time for the 500 Hz and 1000 Hz runs. The dashed lines
		show quadratic least-squares fits to the data for $t \gtrsim 20~\mathrm{ms}$.}
\end{figure}

\begin{figure}[t]
	\centering
	{\color{red} Placeholder for the flame speed plot that shows temperature dependence}
	\caption{\label{fig:flame_speeds_2} Flame front position vs.\ time for the three 500 Hz runs with
		$T_{star} \leq 3 \times 10^8~\mathrm{K}$. The dashed lines show quadratic least-squares fits to the data
		for $t \gtrsim 20~\mathrm{ms}$.}
\end{figure}
